How is experience transformed into memory?

### 2018-08-29 paper/main.tex
(still) working on results [WIP]

% !TEX TS-program = pdflatex
\documentclass{article}
\usepackage[utf8]{inputenc}
\usepackage[english]{babel}
\usepackage[font=small,labelfont=bf]{caption}
\usepackage{geometry}
\usepackage{natbib}
\usepackage{pxfonts}
\usepackage{graphicx}
\usepackage{newfloat}
\DeclareFloatingEnvironment[name={Supplementary Figure},fileext=lof]{suppfigure}

@@

\section*{Results}
We sought to formalize the gists of a naturalistic stimulus (an episode of the \textit{Sherlock} television show) and participants' recountings of that stimulus.
% JRM STOPPED HERE
% - add a general overview
% - some of this seems like it belongs in methods...
% - possible section title change to "Narrative?" -- see author guidelines and prior nature submissions

>>>>

\documentclass{article}
\usepackage[utf8]{inputenc}
\usepackage[english]{babel}
\usepackage[font=small,labelfont=bf]{caption}
\usepackage{geometry}
\usepackage{natbib}
\usepackage{pxfonts}
\usepackage{graphicx}
\usepackage{newfloat}
\usepackage{setspace}
\DeclareFloatingEnvironment[name={Supplementary Figure},fileext=lof]{suppfigure}
\doublespacing

@@

\section*{Results}

We sought to formalize the gists of a naturalistic stimulus (an episode of the \textit{Sherlock} television show) and participants' recountings of that stimulus.
% JRM STOPPED HERE
% - add a general overview
% - some of this seems like it belongs in methods...
% - possible section title change to "Narrative?" -- see author guidelines and prior nature submissions
